Sea: A lightweight data-placement library for Big Data scientific computing

### 2022-04-13 paper/sea-comp/paper.tex
addressed comments

      Data locality ensures that compute tasks are scheduled nearest to where
      the data is located. Historically, storage and compute nodes were distinct
      layers, \TG{missing word?} data transfer to the compute location. Rather than transferring
      large amounts of data over the network to compute tasks, which could incur
      significant overheads, Big Data frameworks ensure that data is stored
      directly on the compute nodes. When a compute task requires access to
      specific data, the scheduler sends the task to the nearest available node
      to the data, thereby minimizing any cost of network-related data
      transfers. This strategy is not only used by Big Data Frameworks such as
      Hadoop MapReduce, Apache Spark, and Dask~\cite{rocklin2015dask}, but also
      enabled by file systems such as HDFS and Alluxio.

@@

      As can be seen in Figure~\ref{fig:sea-comp:benchmarks}, Sea using
      in-memory configuration speeds up execution the majority of the
      conditions. The largest speedups observed can be seen in
      Figure~\ref{fig:sea-comp:processes} at 32 processes, where the speedup is
      nearly 3$\times$. We believe that the speedup is primarily due to the
      contention on Lustre. While each local disk has an average of 5 processes
      trying to write concurrently to it at 32 processes, each Lustre has around
      3 concurrent processes while to it \TG{this sentence doesn't make sense, revise}. Whereas one might assume this means
      Lustre would have less contention overall and should perform better, there
      are significant bandwidth differences to account for between the local
      disks and Lustre (see Table~\ref{table:sea-comp:fs}) that would result in
      improved local disk performance despite increased contention. Furthermore,
      Lustre has a centralized metadata server that is responsible for
      determining which OST is assigned to each block, guaranteeing a certain
      amount of load-balance on the storage disks. This is in contrast with the
      local disks, who do not rely on a metadata server and are selected by Sea
      via a random shuffling.

@@

    The flush-and-evict process may affect overall application parallelism. It
    would depend on how many Sea processes are started on the compute node. If
    only a single instance of Sea is called on a compute node, there will only
    be a single flush and evict process, and therefore, only a single flush and
    evict process will exist \TG{this sentence is circular, revise}. However, if Sea is launched many times on a given
    node, there will be many flush and evict processes which may interfere with
    the application compute. However, our results do not indicate that
    performance is significantly impacted by the presence of a single flush and
    evict process.

>>>>

      Data locality ensures that compute tasks are scheduled nearest to where
      the data is located. Historically, storage and compute nodes were distinct
      layers, transferring data to the compute location whenever necessary. Rather than transferring
      large amounts of data over the network to compute tasks, which could incur
      significant overheads, Big Data frameworks ensure that data is stored
      directly on the compute nodes. When a compute task requires access to
      specific data, the scheduler sends the task to the nearest available node
      to the data, thereby minimizing any cost of network-related data
      transfers. This strategy is not only used by Big Data Frameworks such as
      Hadoop MapReduce, Apache Spark, and Dask~\cite{rocklin2015dask}, but also
      enabled by file systems such as HDFS and Alluxio.

@@

      As can be seen in Figure~\ref{fig:sea-comp:benchmarks}, Sea using
      in-memory configuration speeds up execution the majority of the
      conditions. The largest speedups observed can be seen in
      Figure~\ref{fig:sea-comp:processes} at 32 processes, where the speedup is
      nearly 3$\times$. We believe that the speedup is primarily due to the
      contention on Lustre. While each local disk has an average of 5 processes
      trying to write concurrently to it at 32 processes, each Lustre disk has around
      3 concurrent processes writing to it. Whereas one might assume this means
      Lustre would have less contention overall and should perform better, there
      are significant bandwidth differences to account for between the local
      disks and Lustre (see Table~\ref{table:sea-comp:fs}) that would result in
      improved local disk performance despite increased contention. Furthermore,
      Lustre has a centralized metadata server that is responsible for
      determining which OST is assigned to each block, guaranteeing a certain
      amount of load-balance on the storage disks. This is in contrast with the
      local disks, who do not rely on a metadata server and are selected by Sea
      via a random shuffling.

@@

    The flush-and-evict process may affect overall application parallelism if multiple Sea instances
    are launched on a given node. If
    only a single instance of Sea is called on a compute node, there will only
    be a single flush and evict process. However, if Sea is launched many times on a given
    node, there will be many flush and evict processes which may interfere with
    the application compute. However, our results do not indicate that
    performance is significantly impacted by the presence of a single flush and
    evict process.
